\documentclass[a4paper,9pt]{article}
\usepackage[left=0.5in, right=0.4in, top=0.4in, bottom=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{amssymb}
% Define a reusable section template
\newcommand{\cvsection}[2]{
    \vspace{0.3cm} % Add spacing before each section
    \noindent {\large \textbf{#1}} % Section Title
    \begin{itemize}
        \renewcommand{\labelitemi}{}
        \small #2 % Bullet Points
    \end{itemize}
}
\usepackage{enumitem}
\setlist[itemize,1]{left=-10pt} % Remove extra indentation for first-level items
\setlist[itemize,2]{left=0.8em} % Slightly indent second-level items
\setlist[itemize]{left=0pt, topsep=5pt, itemsep=2pt, parsep=0pt}



\begin{document}

% Header
\noindent{\LARGE \textbf{Raffaello Fornasiere}}

\vspace{0.2cm}
\noindent
\begin{minipage}{\linewidth}
    \begin{center}
        Email: \href{mailto:fornasiere.raffaello@gmail.com}{fornasiere.raffaello@gmail.com} \hfill
        Linkedin: \href{https://linkedin.com/in/raffaello-fornasiere}{raffaello-fornasiere} \hfill
        Website: \href{https://rf-98.com}{rf-98.com}\hfill
        Github: \href{https://github.com/RaffaelloFornasiere}{RaffaelloFornasiere}\hfill
    \end{center}
\end{minipage}

\cvsection{Summary}{
    \item I am an ML research engineer focused on AI safety and interpretability.
    I am currently at LASR Labs, building safety-relevant model organisms and evaluating auditing methods.
    I have previously built an AI assistant with long-term memory and tool integrations for an Anthropic researcher, and served as lead software engineer at an Italian startup.
}

\cvsection{Professional Experience}{
    \item \textbf{AI Safety Researcher} (April 2026 – August 2026)
    \begin{itemize}
        \item My team at LASR Labs has been recently awarded a grant to extend the project for 4 additional months, continuing under the mentorship of \textbf{Stefan Heimersheim}.
        \item Investigating which training variations of model organisms cause mechanistic interpretability methods to fail, to expose blind spots in current auditing benchmarks.
    \end{itemize}

    \item \textbf{Technical AI Safety course facilitator}, BlueDot Impact (May 2026 – June 2026)
    \begin{itemize}
        \item Part-time (7h/week) facilitating two cohorts through BlueDot Impact's Technical AI Safety course, leading weekly discussions on AI Safety.
    \end{itemize}

    \item \textbf{LASR Labs Research Fellow}, LASR Labs (January 2026 – April 2026)
    \begin{itemize}
        \item Selected for a 13-week AI safety research program in London.
        \item Working in a team mentored by \textbf{Stefan Heimersheim} to build more realistic safety-relevant model organisms
        and evaluate whether current auditing/interpretability methods still work.
    \end{itemize}

    \item \textbf{ARENA 7.0 Mentee}, ARENA (January 2026 – February 2026)
    \begin{itemize}
        \item Selected participant in a 5-week full-time bootcamp focused on ML engineering for technical AI safety.
        \item Curriculum covering transformers, reinforcement learning, mechanistic interpretability, and safety evaluations.
        \item Awarded 1st prize at ARENA’s interpretability hackathon.
    \end{itemize}

    \item \textbf{AI Agent Developer}, Freelance for William Saunders, Alignment Science Researcher at Anthropic (May 2025 - December 2025)
    \begin{itemize}
        \item Built an AI assistant that maintains coherent context over months of use, avoiding the repetitive patterns typical of commercial assistants.
        \item Integrated tool add-ons including asynchronous browser use, Google Calendar, and speech-to-speech interfaces.
        \item Tech stack: FastAPI, React, Claude API, RAG, event-driven architecture.
    \end{itemize}
    \item \textbf{Lead Software Engineer - Front-End}, Infiniteloop (October 2022 - August 2025)
    \begin{itemize}
        \item Prototyped AI healthcare applications using LLMs, exploring feasibility for medical report automation (related to my thesis work).
        \item Designed, built and maintained user interfaces using Angular, ensuring seamless integration with JHipster framework.
        \item Developed reusable JHipster framework extensions (e.g., an extended JHipster Criteria API, a custom Spring Data JPA repository for bidirectional relationship synchronization).
        \item Lead the development of different products. 
        \item Mentored two junior developers and promoted best practices to improve code quality.
    \end{itemize}
    \item \textbf{Junior Full Stack Developer}, Prodigys Group (July 2021 - September 2022)
    \begin{itemize}
        \item Developed and maintained both front-end and back-end components using Angular, SpringBoot, and Django.
        \item Optimized database performance through SQL query refactors, reducing execution times from hours to minutes.
    \end{itemize}
}

\cvsection{Education}{
    \item \textbf{Master's in Computer Science and Engineering}, Politecnico di Milano (Graduated July 2024)
    \begin{itemize}
        \item Thesis: Exploring the Potential of Lightweight LLMs for Medication and Timeline Extraction.
        \item Developed a web application integrating LLMs for medical information extraction, \textbf{tested in three Italian hospitals}.
        \item Published research: ``Medical Information Extraction with Large Language Models'' (ACL 2024).
    \end{itemize}
    \item \textbf{Bachelor's in Electronics Engineering}, Università degli Studi di Udine (Graduated July 2020)
    \begin{itemize}
        \item Thesis: Optimization of Digital Circuit Propagation Times Using Genetic Algorithms.
    \end{itemize}
}

\cvsection{Technical Skills}{
    \item \textbf{ML Research \& Engineering:}
    \begin{itemize}
        \item Model training and fine-tuning (SFT, DPO) up to 1B parameters, data pipeline construction and filtering at scale.
        \item Linear probes and classifiers for mechanistic interpretability, LLM-as-judge labelling pipelines.
        \item Transformer internals (TransformerLens, activation hooks), RL and RLHF, safety evaluations and benchmarking.
        \item Libraries: PyTorch, Hugging Face Transformers, TransformerLens, llama.cpp.
    \end{itemize}
    \item \textbf{AI/LLM Integration:}
    \begin{itemize}
        \item LLM APIs (OpenAI, Anthropic Claude), agent development, RAG, prompt engineering, local models (llama.cpp).
    \end{itemize}
    \item \textbf{Languages:}
    \begin{itemize}
        \item Primary: TypeScript/JavaScript, Python, Java.
        \item Also experienced with: C++, SQL.
        \item Others: CSS, HTML. 
    \end{itemize}
    \item \textbf{Frameworks, Libraries and Tools:}
    \begin{itemize}
        \item Back-end: FastAPI, Django, Spring Boot, JHipster.
        \item Front-end: React, Vue.js, Angular.
    \item Others: Docker, Git, Tailwind CSS, Streamlit, Spring Data JPA, Postgres/PostgreSQL, SQLite.
    \end{itemize}
}


\cvsection{Publications}{
    \item \textbf{Medical Information Extraction with Large Language Models} \\
    \textit{Published at ICNLSP-2024, ACL Anthology (A* ranked by CORE, ~20-25\% acceptance rate)} \\
    \url{https://aclanthology.org/2024.icnlsp-1.47/}
    \begin{itemize}
        \item Authors: \textbf{Raffaello Fornasiere}, Nicolò Brunello, Vincenzo Scotti, Mark Carman.
    \end{itemize}
}


\cvsection{Academic Projects}{
    \item \textbf{Medical Image-Caption Matching with Transformers}
    \begin{itemize}
       \item Reimplemented CLIP model from scratch for medical radiology applications using ResNet vision encoder and custom transformer text encoder.
       \item Trained and fine-tuned both models using contrastive learning, pre-trained BERT integration, caption preprocessing, and medical concept augmentation techniques.
       \item Developed evaluation methods for assessing image-caption alignment in medical domain.
    \end{itemize}
    \item \textbf{Online Learning for Dynamic Pricing in E-commerce}
    \begin{itemize}
        \item Exploration work implementing multi-armed bandit algorithms (GP-TS, GP-UCB) with social influence modeling to optimize advertising budget allocation across product campaigns.
    \end{itemize}
    \item \textbf{Deep Learning Projects with CNNs}
    \begin{itemize}
        \item \textbf{Species Classification:} Implemented transfer learning with VGG16/19 and EfficientNet models, applying data augmentation techniques (CutMix, MixUp) and ensemble methods to achieve 86.91\% accuracy on image classification tasks.
        
        \item \textbf{Time Series Classification:} Developed CNN-LSTM hybrid architectures for sequential data analysis, experimenting with preprocessing techniques including normalization and noise augmentation to reach 70\% classification accuracy.
    \end{itemize}
}

\cvsection{Other Experiences}{
    \item \textbf{STAIR Mentor}, St Andrews Impact Research (Feb 2026 – Present)
    \begin{itemize}
        \item Mentoring 2 early career students beginning AI safety research.
    \end{itemize}
    \item \textbf{ML4Good AI Safety Bootcamp}
    \begin{itemize}
        \item Completed EPFL's iteration of the \href{https://www.ml4good.org/}{ML4Good} AI Safety and ML Bootcamp (February 2023).
    \end{itemize}
}

\cvsection{Community Involvement}{
    \item \textbf{Volunteer developer for hometown community}
    \begin{itemize}
        \item Built website to publish local competition status with real-time updates through Telegram bot.
        \item Developed web application to emulate Italian TV game show, managing multiplayer gameplay across mobile devices.
    \end{itemize}
}

\end{document}
